
\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1.7cm]{geometry}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{amsmath,amssymb}
\usepackage{siunitx}
\usepackage[most]{tcolorbox}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{setspace}

\definecolor{DemeterBlue}{HTML}{102A43}
\definecolor{DemeterSky}{HTML}{1F6FEB}
\definecolor{DemeterLight}{HTML}{F4F7FB}
\definecolor{DemeterLine}{HTML}{D9E2EC}
\definecolor{DemeterText}{HTML}{243B53}
\definecolor{DemeterMuted}{HTML}{486581}
\definecolor{DemeterAccent}{HTML}{DCEBFF}

\hypersetup{
  colorlinks=true,
  linkcolor=DemeterSky,
  urlcolor=DemeterSky,
  pdftitle={Demeter Design Reference Environment},
  pdfauthor={OpenAI for Yaroslav}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}
\renewcommand{\arraystretch}{1.22}
\setlength{\headheight}{14pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{DemeterMuted}{Demeter Design Reference Environment v1.0}}
\fancyhead[R]{\textcolor{DemeterMuted}{Psyche mission case}}
\fancyfoot[L]{\textcolor{DemeterMuted}{Prepared for presentation use}}
\fancyfoot[R]{\textcolor{DemeterMuted}{\thepage/\pageref{LastPage}}}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0pt}

\titleformat{\section}{\Large\bfseries\color{DemeterBlue}}{\thesection}{0.6em}{}
\titleformat{\subsection}{\large\bfseries\color{DemeterText}}{}{0em}{}

\newtcolorbox{hero}{
  enhanced,
  colback=DemeterLight,
  colframe=DemeterBlue,
  boxrule=0.8pt,
  arc=3mm,
  left=3mm,right=3mm,top=2.2mm,bottom=2.2mm
}

\newtcolorbox{formulaBox}{
  enhanced,
  breakable,
  colback=white,
  colframe=DemeterLine,
  boxrule=0.5pt,
  arc=2mm,
  left=3mm,right=3mm,top=2mm,bottom=2mm
}

\newcommand{\keynum}[1]{\textcolor{DemeterBlue}{\textbf{#1}}}
\newcommand{\unitau}{\,\mathrm{au}}

\begin{document}

\begin{hero}
{\LARGE\bfseries\color{DemeterBlue} Demeter Design Reference Environment (DRE) v1.0}\\[0.4em]
{\large \color{DemeterText} Unified constants, environmental assumptions, and core equations for first-pass engineering calculations near \textbf{16 Psyche}.}\\[0.8em]
\textcolor{DemeterMuted}{Purpose: freeze a single team-wide baseline for transport, communications, AI operations, thermal analysis, and mining robotics.}
\end{hero}

\vspace{0.6em}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
Adopted operating context & Demeter is modeled as a deep-space settlement operating near Psyche in hard vacuum, with low gravity, delayed Earth communications, and strong dependence on local autonomy. \\
Key engineering assumption & For thermal calculations, use \(A=0.15\) and \(\varepsilon=0.90\). For contact-mechanics and robot design, keep a conservative gravity baseline of \(g_{ref}=\SI{0.08}{m/s^2}\). \\
\end{tabularx}

\section{Fundamental constants}

\begin{center}
\begin{tabularx}{0.98\textwidth}{@{}l c >{\raggedleft\arraybackslash}X l@{}}
\toprule
Quantity & Symbol & Value & Units \\
\midrule
Speed of light & \(c\) & \num{2.99792458e8} & \si{m/s} \\
Astronomical unit & \(1\,\mathrm{au}\) & \num{1.495978707e11} & \si{m} \\
Gravitational constant & \(G\) & \num{6.67430e-11} & \si{m^3.kg^{-1}.s^{-2}} \\
Stefan--Boltzmann constant & \(\sigma\) & \num{5.670374419e-8} & \si{W.m^{-2}.K^{-4}} \\
Solar constant at 1 au & \(S_{1au}\) & \num{1361.6} & \si{W/m^2} \\
\bottomrule
\end{tabularx}
\end{center}

\section{Reference Psyche parameters}

\begin{center}
\begin{tabularx}{0.98\textwidth}{@{}l c >{\raggedleft\arraybackslash}X l@{}}
\toprule
Quantity & Symbol & Value & Units \\
\midrule
Perihelion distance & \(q\) & \num{2.54} & au \\
Mean working distance & \(a\) & \num{2.93} & au \\
Aphelion distance & \(Q\) & \num{3.32} & au \\
Effective diameter & \(D_{eff}\) & \num{226} & km \\
Effective radius & \(R_{eff}\) & \num{1.13e5} & m \\
Reference mass & \(M\) & \num{2.41e19} & kg \\
Bulk density & \(\rho\) & \num{3990} & \si{kg/m^3} \\
Rotation period & \(P_{rot}\) & \num{4.196} & h \\
Bond albedo (design) & \(A\) & \num{0.15} & --- \\
Emissivity (design) & \(\varepsilon\) & \num{0.90} & --- \\
Conservative nominal gravity baseline & \(g_{ref}\) & \num{0.08} & \si{m/s^2} \\
\bottomrule
\end{tabularx}
\end{center}

\section{Core equations}

\begin{formulaBox}
\[
S(r)=\frac{S_{1au}}{r^2}
\qquad
T_{eq}=\left(\frac{(1-A)S}{4\varepsilon\sigma}\right)^{1/4}
\qquad
T_{ss}=\left(\frac{(1-A)S}{\varepsilon\sigma}\right)^{1/4}
\]
\[
\mu = GM
\qquad
\omega = \frac{2\pi}{P_{rot}}
\qquad
g = \frac{\mu}{r^2}
\qquad
a_{cf}=\omega^2 r
\qquad
g_{eff}=g-a_{cf}
\qquad
v_{esc}=\sqrt{\frac{2\mu}{r}}
\]
\[
t_{light}=\frac{d}{c}
\]
\end{formulaBox}

\section{Derived thermal environment}

Using \(A=0.15\) and \(\varepsilon=0.90\):

\begin{center}
\begin{tabularx}{0.98\textwidth}{@{}l >{\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash}X@{}}
\toprule
Case & \(r\) [au] & Solar flux \(S\) [\si{W/m^2}] & \(T_{eq}\) [K] & \(T_{ss}\) [K] \\
\midrule
Perihelion & 2.54 & 211.048 & 172.176 & 243.493 \\
Mean working orbit & 2.93 & 158.604 & 160.308 & 226.710 \\
Aphelion & 3.32 & 123.530 & 150.598 & 212.978 \\
\bottomrule
\end{tabularx}
\end{center}

\begin{hero}
\textbf{Interpretation.} Demeter operates in a cold radiative environment: even at the mean orbit, solar input is only about \keynum{158.6 \si{W/m^2}}, far below Earth orbit. Thermal design must therefore emphasize insulation, radiator control, and heat recapture rather than atmospheric heat exchange.
\end{hero}

\section{Surface mechanics at Psyche}

Spherical-reference estimates at \(R_{eff}=\SI{113000}{m}\):

\begin{center}
\begin{tabularx}{0.98\textwidth}{@{}l c >{\raggedleft\arraybackslash}X l@{}}
\toprule
Quantity & Symbol & Value & Units \\
\midrule
Standard gravitational parameter & \(\mu\) & \num{1.6085063e9} & \si{m^3/s^2} \\
Angular velocity & \(\omega\) & \num{4.1595e-4} & \si{rad/s} \\
Surface gravity at \(R_{eff}\) & \(g\) & \num{0.12597} & \si{m/s^2} \\
Centrifugal reduction at \(R_{eff}\) & \(a_{cf}\) & \num{0.01955} & \si{m/s^2} \\
Effective gravity at \(R_{eff}\) & \(g_{eff}\) & \num{0.10642} & \si{m/s^2} \\
Escape speed at \(R_{eff}\) & \(v_{esc}\) & \num{168.728} & \si{m/s} \\
\bottomrule
\end{tabularx}
\end{center}

\begin{formulaBox}
\textbf{Design note.} The computed \(g_{eff}\) is a spherical-reference value. For mining robots, anchoring, drilling, and contact-force envelopes, the project baseline remains the more conservative \(g_{ref}=\SI{0.08}{m/s^2}\). This makes the design robust against local topography, shape irregularity, and operational uncertainty.
\end{formulaBox}

\section{Earth--Psyche communication latency}

\begin{center}
\begin{tabularx}{0.98\textwidth}{@{}l >{\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash}X >{\raggedleft\arraybackslash}X@{}}
\toprule
Case & Distance [million miles] & Distance [\(10^9\) m] & One-way light time [min] \\
\midrule
Minimum separation & 186 & 0.299337984 & 16.641 \\
Maximum separation & 372 & 0.598675968 & 33.283 \\
\bottomrule
\end{tabularx}
\end{center}

\begin{hero}
\textbf{Operational consequence.} No critical subsystem should assume real-time control from Earth. Demeter must be designed around \textbf{local autonomy}, \textbf{delay-tolerant networking}, and \textbf{human--AI teaming} under multi-minute one-way latency.
\end{hero}

\section{Recommended frozen baseline for team calculations}

\begin{center}
\begin{tabularx}{0.98\textwidth}{@{}l >{\raggedleft\arraybackslash}X l@{}}
\toprule
Baseline quantity & Value & Units \\
\midrule
Working solar distance & 2.93 & au \\
Perihelion / aphelion envelope & 2.54 / 3.32 & au \\
Solar flux at working orbit & 158.604 & \si{W/m^2} \\
Reference mass & \num{2.41e19} & kg \\
Reference gravitational parameter & \num{1.6085063e9} & \si{m^3/s^2} \\
Rotation period & 4.196 & h \\
Spherical-reference effective gravity & 0.10642 & \si{m/s^2} \\
Conservative project gravity baseline & 0.08 & \si{m/s^2} \\
Escape speed & 168.728 & \si{m/s} \\
Thermal equilibrium temperature at working orbit & 160.308 & K \\
Subsolar temperature at working orbit & 226.710 & K \\
One-way Earth latency envelope & 16.64--33.28 & min \\
External environment & Hard vacuum & qualitative \\
\bottomrule
\end{tabularx}
\end{center}

\section{Engineering implications}

\begin{itemize}[leftmargin=1.4em]
  \item \textbf{Anchoring is mandatory.} Low gravity makes excavation, drilling, and reaction-force management fundamentally different from terrestrial mining.
  \item \textbf{External heat transfer is radiative.} There is no atmospheric convection; subsystem thermal models should be radiator- and insulation-centric.
  \item \textbf{Local autonomy is non-optional.} Earth latency in the tens of minutes rules out real-time teleoperation for safety-critical actions.
  \item \textbf{Use one baseline across the whole team.} A unified environment model prevents contradictions between transport, communications, AI, and robotics slides.
\end{itemize}

\vfill
\textcolor{DemeterMuted}{Source basis: public NASA Psyche mission information and frozen engineering assumptions adopted for the Demeter concept study.}

\end{document}
